Specific leaf mass explains difference in biomass partitioning between woody plant functional types

### 2014-10-14 manuscript/draftpaper.Rnw
Makefile fixed; analysis moved to statanalysis (and added to makefile)

\begin{enumerate}
\item Importance of biomass allocation in global vegetation models \cite{ise_comparison_2010}, feedback on fluxes of CO2, lifetime of C in the system \cite{friend_carbon_2014}.

>>>>

\begin{enumerate}
\item The importance of biomass allocation in global vegetation models \cite{ise_comparison_2010}, feedback on fluxes of CO2, lifetime of C in the system \cite{friend_carbon_2014}, which depends on partitioning of biomass into short-lived foliage vs. long-lived woody pools.
